Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline

### 2016-11-29 Ben_Manuscripts/Paper1/Paper1_Outline.tex
Edited outline

\documentclass{article}
\title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Michael R. Shirts} % usually the PI would be the last author.
\begin{document}
	\bibliographystyle{ieeetr}
	\maketitle
	\section{Introduction}
%MRS: make sure the introduction asks all the questions that will be answered by the results presented, and doesn't raise questions that are never brought up again. 	
%MRS: possibly we want to look at the more detailed X-ray diffraction patterns, but that may not be feasible on the timescale.
	Nanostructured membrane materials have become increasingly popular in desalination and wastewater treatment applications because they offer the ability to control membrane architecture at the atomic scale.
	\begin{itemize}
		\item Current state-of-the-art reverse osmosis membranes are dense and unstructured with tortuous and polydisperse pores which lead to inconsistent performance
		\item Tortuosity and polydispersity drive up energy requirements which strain developing regions and contribute strongly to CO2 emissions
		\item With nanostructured materials, solute rejecting pores can be tuned uniformly -- drives down energy requirements
	\end{itemize}

	Development of nanostructured materials has been limited by the ability to synthesize and scale various fundamentally sound technologies.
	\begin{itemize}
		\item Leading technologies and their limitations:
		\begin{itemize}
			\item Graphene sheets -atomically thick which gives excellent permeability but defects during manufacturing severely impact performance
			\item Carbon Nanotubes - MD studies are promising but synthetic techniques unable to achieve necessary alignment and pore monodispersity
		\end{itemize}
	\end{itemize} 
	Self assembling lyotropic liquid crystals (LLCs) share the characteristic ability of nanostructured membrane materials to create highly ordered structures with the benefits of low cost and synthetic techniques feasible for large scale production.
	\begin{itemize}
		\item Forms lamellar, bicontinuous cubic and hexagonal phase based on solution composition
		\item My monomer form two types of self assembled LLCs - thermotropic (Colh) and lyotropic (HII) - explain difference 
		\item Hydrophilic regions point towards pore centers
		\item Until recently, they could not be aligned - hindered progress
		\item Yale aligns them
		\item LLC HII phase membranes offer potential for high permeability and selectivity which equals low energy consumption
		\item This paper will focus on the development of a model of the colh phase since it is a simpler starting point and has just as much experimental data
	\end{itemize}
%MRS: might want to include effective pore radius.
%BJC: I'm not sure how to include the pore radius since we don't have a clear method for its measurement (experimentally and consequently
%via simulations). I don't know that we can answer that question which is why I didn't pose it in the intro	
%MRS2: if no measurement experimentally, don't need one for simulation at this point!
	Constructing a molecular model may give a clearer picture of the microscopic structure of LLC membranes which will change how we think about their design.
	\begin{itemize}
		\item The arrangement of sodium ions in the channels is thought to be confined to the pore walls. It is possible they are arranged more randomly
		\begin{itemize}
			\item This could change how one thinks about molecules diffusing through membrane
			\item Could also be a difference between lyotropic and thermotropic phases
		\end{itemize}
		%BJC - I'm likely going to cut this since I cannot answer this question definitively - unless we take an approach based on enthalpy differences and structural comparisons (pore-to-pore distance and x-ray scattering data). We probably have enough information for a speculative answer, but I don't know if that should be included in the paper
                %MRS: I think it's probably useful to report which arrangements are stable and give consistent pore-to-pore distances. Also can help answer the questions whether there are distinct well-separated ``layers'', or if it's more complicated. 
		\item How many monomers are in a layer?
		\begin{itemize}
			\item There is no clear answer to this question in literature. I'd like to confirm or deny past predictions
		\end{itemize}
	\end{itemize}

@@

	An ensemble of characteristic, low-energy vacuum monomer configurations were constructed by applying a simulated annealing process to a parameterized monomer.
	\begin{itemize}
		\item Initially parameterized monomer gives unfavorable structure
		\item Structure cooled from 1000 to 50 K over 10 nanoseconds
		\item Result not global minimum but close enough for structure building
		\item Multiple configurations saved from annealing trajectory to prove independence of starting config
                 %MRS: say what you mean by reparameterized.  Charges recalculated? Are the charges different from configuration to configuration (hopefully not).  Were multiple configurations used in the reparameterization?
		\item New configurations reparamaterized
	\end{itemize}

@@

>>>>

\documentclass{article}
\title{Predicting Transport in Lyotropic Liquid Crystal Membranes with Molecular Dynamics Simulations -- Outline}
\author{Benjamin J. Coscia \and Douglas L. Gin \and Richard D. Noble \and Michael R. Shirts} 
\begin{document}
	\bibliographystyle{ieeetr}
	\maketitle
	\section{Introduction}
%MRS: make sure the introduction asks all the questions that will be answered by the results presented, and doesn't raise questions that are never brought up again. 	
%MRS: possibly we want to look at the more detailed X-ray diffraction patterns, but that may not be feasible on the timescale.
	Nanostructured membrane materials have become increasingly popular in desalination and wastewater treatment applications because they offer the ability to control membrane architecture at the atomic scale.
	\begin{itemize}
		\item Current state-of-the-art reverse osmosis membranes are dense and unstructured with tortuous and polydisperse pores which lead to inconsistent performance
		\item Tortuosity and polydispersity drive up energy requirements which strain developing regions and contribute strongly to CO2 emissions
		\item With nanostructured materials, solute rejecting pores can be tuned uniformly -- drives down energy requirements
	\end{itemize}

	Development of nanostructured materials has been limited by the ability to synthesize and scale various fundamentally sound technologies.
	\begin{itemize}
		\item Leading technologies and their limitations:
		\begin{itemize}
			\item Graphene sheets -atomically thick which gives excellent permeability but defects during manufacturing severely impact performance
			\item Carbon Nanotubes - MD studies are promising but synthetic techniques unable to achieve necessary alignment and pore monodispersity
		\end{itemize}
	\end{itemize} 
	Self assembling lyotropic liquid crystals (LLCs) share the characteristic ability of nanostructured membrane materials to create highly ordered structures with the benefits of low cost and synthetic techniques feasible for large scale production.
	\begin{itemize}
		\item Forms lamellar, bicontinuous cubic and hexagonal phase based on solution composition
		\item My monomer form two types of self assembled LLCs - thermotropic (Colh) and lyotropic (HII) - explain difference % actually explain 
		\item Hydrophilic regions point towards pore centers
		\item Until recently, they could not be aligned - hindered progress
		\item Yale aligns them
		\item LLC HII phase membranes offer potential for high permeability and selectivity which equals low energy consumption
		\item This paper will focus on the development of a model of the colh phase since it is a simpler starting point and has just as much experimental data
	\end{itemize}
%MRS: might want to include effective pore radius.
%BJC: I'm not sure how to include the pore radius since we don't have a clear method for its measurement (experimentally and consequently
%via simulations). I don't know that we can answer that question which is why I didn't pose it in the intro	
%MRS2: if no measurement experimentally, don't need one for simulation at this point!
	Constructing a molecular model may give a clearer picture of the microscopic structure of LLC membranes which will change how we think about their design.
	\begin{itemize}
		\item The arrangement of sodium ions in the channels is thought to be confined to the pore walls. It is possible they are arranged more randomly
		\begin{itemize}
			\item This could change how one thinks about molecules diffusing through membrane
			\item Could also be a difference between lyotropic and thermotropic phases
		\end{itemize}
		%BJC - I'm likely going to cut this since I cannot answer this question definitively - unless we take an approach based on enthalpy differences and structural comparisons (pore-to-pore distance and x-ray scattering data). We probably have enough information for a speculative answer, but I don't know if that should be included in the paper
                %MRS: I think it's probably useful to report which arrangements are stable and give consistent pore-to-pore distances. Also can help answer the questions whether there are distinct well-separated ``layers'', or if it's more complicated. 
		%BJC : try five
		\item How many monomers are in a layer?
		\begin{itemize}
			\item There is no clear answer to this question in literature. I'd like to confirm or deny past predictions
		\end{itemize}
	\end{itemize}

@@

	An ensemble of characteristic, low-energy vacuum monomer configurations were constructed by applying a simulated annealing process to a parameterized monomer.
	\begin{itemize}
		\item Initially parameterized monomer gives unfavorable structure
		\item Structure cooled from 1000 to 50 K over 10 nanoseconds
		\item Result not global minimum but close enough for structure building
		\item Multiple configurations saved from annealing trajectory to prove independence of starting config
                 %MRS: say what you mean by reparameterized.  Charges recalculated? Are the charges different from configuration to configuration (hopefully not).  Were multiple configurations used in the reparameterization?
		%BJC: Openeye software to get the best charge for multiple configurations.
		\item New configurations reparamaterized
	\end{itemize}

@@

%BJC: don't explicity say azimuthal
